Asteroseismology {\it sans Fourier}: soon to be crushed by DFM

### 2017-06-30 paper/paper.tex

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.1
\documentclass{aastex61}

@@

\author{David W. Hogg}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA }
\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA }
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany }

@@

\section{Introduction} \label{sec:intro}

>>>>

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.1
\documentclass[modern]{aastex61}

@@

\author[0000-0003-2866-9403]{David W. Hogg}
\affiliation{Center for Computational Astrophysics, Flatiron Institute, 162 Fifth Ave, New York, NY 10010, USA}
\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, room 1005, New York, NY 10003, USA }
\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA }
\affiliation{Max-Planck-Institut f\"ur Astronomie, K\"onigstuhl 17, D-69117 Heidelberg, Germany }

@@

\section{Introduction}\label{sec:intro}

Asteroseismology is performed by taking continuous, excellent data.

Parameter estimation is done by looking at the FT of the time-domain data.

The FT is much cleaner when the data is regularly spaced, close to
homoskedastic, and taken identically.

For example, the FT of the data is the multiply of the FT of the star
with the FT of the exposure-time window, so the whole project breaks
if the exposure time is varied.

For another example, there is no traditional way to do
asteroseismology with sparse-in-time data, like that which will be
produced by LSST and Gaia.

For yet another: Time-localized outlers are death in the Fourier domain.

But in asteroseismology we are only trying to learn a very small number
of scalars from the light curve. Do we really need to beat the light curve
against every possible period?

Finally: Stars are damned coherent. Red giants, in particular, show little
or no sign of decoherence over the entire duration of the Kepler mission.
That should make life better; how?

Here we capitalize on the near-coherence of the modes over reasonable
time periods (and the magic of Gaussians) to perform asteroseismic
parameter estimation in the time domain, without any use of the
Fourier transform.

\section{Method}\label{sec:method}
